\textbf{ Discovery of a disrupting open cluster far into the Milky Way halo:\\ a recent star formation event in the leading arm of the Magellanic stream?}

### 2018-11-10 ms.tex
new figures

\begin{figure}[t]
\centering
%\includegraphics[width=8cm]{gass_mlatmlon.pdf}
\includegraphics[width=8cm]{figures/gass_maps_v3.pdf}
\caption{GASS \hi column density in the region of LA II, shown in three different velocity slices (corresponding to and indicated in each panel).
The coordinate system is the Magellanic stream spherical coordinate system defined in \cite{Nidever:2008}, and the units of $L_{\rm MS}$ and $B_{\rm MS}$ are degrees.
The colorbar shows the column density of \hi in units of $10^19~\textrm{atoms}~\textrm{cm}^{-2}$.
The red circle marks the position of \clustername.}
\label{fig:gass_maps}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=8cm]{figures/gass_vlsrmlon.pdf}
\caption{The position-velocity diagram of GASS \hi Gaussian centers in the same region as \figurename~\ref{fig:gass_maps}, showing the line-of-sight velocity (in the local standard of rest frame) of gas near \clustername.
Note that the densest gas at the longitude of \clustername\ (vertical line) appears to be associated with the lower velocity filaments seen at lower longitudes $L_{\textrm{MS}} \lesssim 60^\circ$, which may be decelerated gas associated with the Magellanic stream.
}
\label{fig:gasspv}
\end{figure}

>>>>

\begin{figure}[t]
\centering
%\includegraphics[width=8cm]{gass_mlatmlon.pdf}
\includegraphics[width=8cm]{figures/gass_maps_v3.pdf}
\caption{GASS \hi column density in the region of LA II, shown in three different velocity slices (corresponding to and indicated in each panel).
The coordinate system is the Magellanic stream spherical coordinate system defined in \cite{Nidever:2008}, and the units of $L_{\rm MS}$ and $B_{\rm MS}$ are degrees.
The colorbar shows the column density of \hi in units of $10^{19}~\textrm{atoms}~\textrm{cm}^{-2}$.
The red circle marks the position of \clustername.}
\label{fig:gass_maps}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=8cm]{figures/gass_vlsrmlon.pdf}
\caption{The position-velocity diagram of GASS \hi Gaussian centers in the same region as \figurename~\ref{fig:gass_maps}, showing the line-of-sight velocity (in the local standard of rest frame) of gas near \clustername.
Here the colorbar shows the gas density in units of $10^{18}~\textrm{atoms}~\textrm{cm}^{-2}\,\textrm{deg}$.
Note that the densest gas at the longitude of \clustername\ (vertical line) appears to be associated with the lower velocity filaments seen at lower longitudes $L_{\textrm{MS}} \lesssim 60^\circ$, which may be decelerated gas associated with the Magellanic stream.
}
\label{fig:gasspv}
\end{figure}
